SPIDERMAN: an open source code to model phase curves and secondary eclipses.

### 2017-07-16 ms.tex
Update on Overleaf.
new plot

For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well ((wakeford reff)). Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however there might be concerns that if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.

@@

>>>>

For HST systematics, where the major sources of error are fairly well understood, a parametrised systematics model of this form works well \citet{Wakeford2016}. Alternatively, detailed instrumental models can recover the same features with fewer free parameters, however there might be concerns that if the form of the systematics changes over time then this approach might underestimate the uncertainty in the shape of the systematics and thus artificially constrain the planet models.

@@

\begin{table}{
			\caption{The full results from the MCMC fit both with and without planetary limb darkening included.}
			\begin{center}
				\begin{tabular}{c c}
					\hline
					\hline
					Central wavelength &   log10(xi)  \\
					(microns) & \\
					\hline
1.1425 & -0.32 $\pm$ 0.27 \\
1.1775 & -0.51 $\pm$ 0.32 \\
1.2125 & -0.00 $\pm$ 0.18 \\
1.2475 & -0.20 $\pm$ 0.19 \\
1.2825 & -0.74 $\pm$ 0.39 \\
1.3175 & -0.32 $\pm$ 0.19 \\
1.3525 & -0.82 $\pm$ 0.62 \\
1.3875 & -0.07 $\pm$ 0.20 \\
1.4225 & -0.09 $\pm$ 0.34 \\
1.4575 & -0.71 $\pm$ 0.31 \\
1.4925 & -0.42 $\pm$ 0.17 \\
1.5275 & -0.76 $\pm$ 0.37 \\
1.5625 & -0.43 $\pm$ 0.14 \\
1.5975 & -0.66 $\pm$ 0.25 \\
1.6325 & -0.59 $\pm$ 0.19 \\
\end{tabular}
\end{center}
\label{tab:results}
}
\end{table}

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{img/all_models.pdf}
		\caption{This alright fit to Xi as a function of wavelength. blue: flat line, green: gradient function, orange: step function}
		\label{fig:best_fit_flux}
	\end{center}
\end{figure}

The flat model gave a value of -0.36 - note that this is a good match to the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF

The best fitting gradient model had values -0.8606214   0.84938152 and gave a chi2 of 8.8 (RCHI2 0.67) with 13 DOF

The best fitting model was the step function model with a dividing wavelength of 1.4225 microns, and step values of -0.5242412 -0.2149221. This gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.

While we find that there is weak evidence for a trend with wavelength in the data, the flat line model provides a satisfactory fit to the data.
